\documentclass[journal]{IEEEtran}
\IEEEoverridecommandlockouts

% Packages
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{automata, positioning, arrows.meta}

\begin{document}

\title{Parser-Layer Circuit Breaker: Preserving QoS in MEC-enabled V2X Networks against ASN.1 Structural Attacks}

\author{\IEEEauthorblockN{Yi-Hung Lu}
\IEEEauthorblockA{\textit{Department of Information Security} \\
\textit{National Sun Yat-sen University (NSYSU)}\\
Kaohsiung, Taiwan \\
M143140012@student.nsysu.edu.tw}
}

\maketitle

\begin{abstract}
Vehicle-to-Everything (V2X) communications increasingly rely on Multi-access Edge Computing (MEC) to meet stringent low-latency requirements. However, the complexity of Abstract Syntax Notation One (ASN.1) parsers, specifically those utilizing Unaligned Packed Encoding Rules (UPER), introduces a critical vulnerability to algorithmic complexity attacks (CWE-674). Maliciously crafted messages with deep structural nesting can exhaust MEC CPU resources, leading to Head-of-Line (HoL) blocking and severe Quality of Service (QoS) degradation for legitimate traffic. This paper proposes a Parser-Layer Circuit Breaker for QoS Preservation, utilizing an Adaptive Finite State Machine (FSM) and an $\mathcal{O}(N)$ structural frequency anomaly detector. By shifting the defense to a lightweight edge-layer sampling mechanism, our approach achieves near-zero inspection overhead during nominal operations while providing millisecond-level mitigation under attack. Experimental results demonstrate that the proposed hybrid defense effectively suppresses P99 tail latency from 0.18 ms to 0.03 ms, ensuring system stability even under high-intensity structural attacks.
\end{abstract}

\begin{IEEEkeywords}
V2X Security, ASN.1 Parser, Algorithmic Complexity Attack, Multi-access Edge Computing (MEC), Quality of Service (QoS), Tail Latency.
\end{IEEEkeywords}

\section{Introduction}

The rapid evolution of Cooperative Intelligent Transport Systems (C-ITS) has established Vehicle-to-Everything (V2X) communication as a cornerstone for future autonomous and semi-autonomous driving. Safety-critical applications, such as platooning, cooperative intersection management, and vulnerable road user (VRU) protection, demand ultra-low-latency message exchange, typically requiring end-to-end delays below 10 ms. To meet these stringent QoS constraints, Multi-access Edge Computing (MEC) has emerged as a vital architectural component, offloading complex computational tasks—such as message parsing, certificate verification, and threat analysis—from On-Board Units (OBUs) to edge processing nodes.

V2X messages, including Cooperative Awareness Messages (CAM) and Decentralized Environmental Notification Messages (DENM), are defined using Abstract Syntax Notation One (ASN.1) and encoded with Unaligned Packed Encoding Rules (UPER). While UPER provides high bandwidth efficiency, its bit-oriented nature and support for recursive structures introduce significant security challenges. Specifically, ASN.1 parsers are susceptible to algorithmic complexity attacks, categorized as CWE-674. By crafting malicious payloads with deeply nested sequences or choice-based recursive structures, an adversary can trigger infinite recursion or exponential object tree expansion. In an MEC environment, such "structural bombs" can exhaust CPU resources and memory bandwidth, leading to Head-of-Line (HoL) blocking. This results in severe latency amplification for legitimate safety messages queued behind a malicious packet undergoing expensive parsing, potentially compromising the safety of the vehicular network.

Conventional security mechanisms, such as deep packet inspection (DPI) and signature-based filtering, often introduce a deterministic "inspection tax" that persists even during nominal operations. For MEC nodes processing high-volume V2X traffic, this continuous overhead can degrade system jitter and inflate P99 tail latency, which is critical for real-time safety guarantees. There is a fundamental conflict between the requirement for exhaustive security verification at the parser layer and the need for low-overhead packet forwarding.

To address this challenge, we propose a \textit{Parser-Layer Circuit Breaker for QoS Preservation}. Unlike traditional static filters, our approach utilizes an Adaptive Finite State Machine (FSM) coupled with an $\mathcal{O}(N)$ structural frequency anomaly detector. By leveraging the entropy discrepancy between legitimate cryptographic payloads and the repetitive structural padding required for recursion-based attacks, the system dynamically modulates its inspection intensity. During peace time, the circuit breaker minimizes overhead through probabilistic sampling, transitioning to full-scale inspection only when a structural anomaly is detected. This allows the system to maintain near-zero overhead during nominal conditions while effectively clamping tail latency under attack.

The primary contributions of this paper are as follows:
\begin{itemize}
    \item We characterize the impact of ASN.1 structural complexity attacks on the QoS of MEC-enabled V2X networks, demonstrating how parser-layer exhaustion leads to HoL blocking.
    \item We propose a lightweight, $\mathcal{O}(N)$ anomaly detector that identifies structural recursion patterns without relying on specific attack signatures or expensive cryptographic verification.
    \item We design an Adaptive Circuit Breaker FSM that balances security and QoS by dynamically adjusting the inspection rate based on the detected threat environment.
    \item We provide an empirical evaluation using the Vanetza V2X stack, quantifying the effectiveness of the proposed mechanism in suppressing P99 tail latency and mitigating the "First-Miss Penalty" through a hybrid defense-in-depth architecture.
\end{itemize}


\section{Background and Threat Model}

\subsection{Background: V2X, ASN.1, and MEC}

V2X communication systems rely on a strictly defined protocol stack where the Facilities layer handles the generation and parsing of standardized messages such as CAM and DENM payloads. These messages are defined using ASN.1, a flexible interface description language that supports complex data types, including optional fields and recursive structures. To achieve the high bandwidth efficiency required for wireless vehicular environments, these messages are encoded using UPER.

In an MEC-enabled architecture, the edge server acts as a high-performance proxy that intercepts and processes V2X traffic to support real-time safety applications. A critical task of the MEC node is the presentation-layer parsing of ASN.1 payloads. This process involves the expansion of bit-oriented UPER streams into in-memory object trees that can be further processed by the application logic. 

Recursive parsing structures are common in V2X certificates and security headers (e.g., IEEE 1609.2). For example, a certificate may contain a sequence of attributes or optional choice fields that, if maliciously defined, allow for deeply nested object trees. In traditional parsers, each level of nesting triggers a stack frame allocation or a recursive function call. Under CWE-674 (Algorithmic Complexity / Infinite Recursion) attacks, an adversary exploits these recursive definitions to trigger parser-level complexity amplification. A small malicious payload (e.g., a few hundred bytes) can force the parser to perform thousands of recursive operations, consuming disproportionate CPU cycles and memory bandwidth.

In high-throughput MEC processing pipelines, this resource exhaustion manifests as HoL blocking. Since the MEC node typically processes packets in a first-in-first-out (FIFO) or priority-queued manner at the presentation layer, a single "structural bomb" undergoing an expensive parsing operation effectively blocks the processing pipeline. Legitimate, time-sensitive safety messages queued behind the malicious packet suffer from catastrophic latency jitter, even if the MEC node is not volumentrically saturated.

\subsection{Threat Model}

The primary objective of this research is to mitigate parser-layer resource exhaustion attacks that compromise the QoS of MEC-enabled V2X networks.

\subsubsection{Scope of Attack}
The threat model focuses on ASN.1 structural complexity attacks (e.g., CWE-674). The adversary is assumed to be a compromised or malicious OBU or a roadside entity capable of injecting syntactically valid but structurally malicious UPER-encoded messages into the network. These messages exploit optional or choice-based recursive structures (e.g., nested sequence of containers) to force the parser into deep recursion or exhaustive memory allocation. 

The attacker's goal is not necessarily to crash the MEC node but to introduce sufficient latency jitter to disrupt safety-critical V2X applications. By carefully crafting the nesting depth, the attacker can maximize the "first-miss" impact where the malicious payload is partially processed before being rejected or causing a timeout.

\subsubsection{Attacker Capabilities and Constraints}
1) \textit{Structural Manipulation:} The attacker can manipulate the ASN.1 tree depth to exceed typical operational limits.
2) \textit{Entropy Constraint:} Constructing deeply nested ASN.1 structures within maximum transmission unit (MTU) limits often necessitates repetitive byte patterns (structural padding) to satisfy length determinants and choice indices. 
3) \textit{Network Layer:} The attack is carried out at the application/presentation layer but manifests as a resource exhaustion denial-of-service (DoS) at the MEC processing node. 

\subsubsection{Out-of-Scope Boundaries}
To maintain a focused research scope, the following attack vectors are explicitly considered out-of-scope:
\begin{itemize}
    \item \textbf{Volumetric DDoS:} We do not address general L3/L4 flooding attacks (e.g., UDP floods) aimed at saturating network bandwidth.
    \item \textbf{Cryptographic Compromise:} We assume the underlying cryptographic primitives (e.g., ECDSA) and PKI structures are secure; the attack targets the parser before or during certificate verification.
    \item \textbf{Replay and Sybil Attacks:} While critical in V2X, these are handled by the security envelope and MIS (Misbehavior Detection) layers, not the parser-layer circuit breaker.
    \item \textbf{PKI/CA Compromise:} Attacks targeting the root of trust or certificate issuance process are beyond the scope of presentation-layer defense.
\end{itemize}


\section{Related Work}

\subsection{V2X Security and Misbehavior Detection}
Security in vehicular ad-hoc networks (VANETs) has traditionally focused on public key infrastructure (PKI) and certificate management to ensure message authenticity and non-repudiation. Standards such as IEEE 1609.2 define the security envelope for V2X messages, utilizing elliptic curve cryptography (ECC) for digital signatures % TODO: Add citation here. 
Beyond cryptographic verification, misbehavior detection systems (MDS) have been proposed to identify semantic anomalies, such as position "ghosting" or impossible speed jumps % TODO: Add citation here. 
However, most existing MDS architectures operate at the application layer, assuming that the underlying message has already been successfully parsed. Our work addresses a lower-level vulnerability in the presentation layer that precedes semantic analysis.

\subsection{ASN.1 Parser Hardening and UPER Security}
The security of ASN.1 parsers is a long-standing concern in telecommunications and networking. Research into parser hardening typically involves the use of formal methods or safe-language implementations (e.g., Rust) to prevent buffer overflows and memory corruption % TODO: Add citation here. 
For UPER parsers specifically, hardening often focuses on enforcing MTU limits and validating length determinants during the bit-stream expansion process. While modern patches for tools like \texttt{asn1c} mitigate infinite recursion by imposing static recursion depth limits % TODO: Add citation here, 
these limits are often set conservatively to avoid breaking complex legitimate structures. Furthermore, application-layer patches do not prevent the CPU resource exhaustion that occurs during the recursive descent itself, which is where our proposed edge-layer pre-filter provides critical protection.

\subsection{Algorithmic Complexity Attacks}
Algorithmic complexity attacks (CWE-674) exploit the worst-case performance of algorithms to trigger DoS. Early research in this area highlighted vulnerabilities in hash table collisions and regular expression engines % TODO: Add citation here. 
In the context of tree-structured data formats like XML and ASN.1, these attacks leverage "structural bombs" or "billion laughs" variants to trigger exponential expansion or deep recursion. While volumetric DoS attacks are well-studied in V2X % TODO: Add citation here, 
the specific threat of parser-layer complexity attacks—where a low-bandwidth stream causes high-CPU load—remains under-addressed in vehicular environments. Our approach specifically targets the entropy-based detection of such structural patterns at the network edge.

\subsection{QoS-aware Edge Security and MEC Constraints}
The integration of MEC into V2X architectures introduces new constraints for security engineering. MEC nodes must process high-throughput traffic with deterministic latency to support safety-critical functions % TODO: Add citation here. 
Research into QoS-aware security often involves offloading expensive verification tasks to hardware accelerators or utilizing eBPF/XDP for high-speed packet filtering % TODO: Add citation here. 
However, DPI for complex formats like ASN.1 remains computationally expensive. Our work contributes to this domain by introducing a systems-oriented circuit breaker mechanism that balances security intensity with real-time QoS requirements through adaptive sampling and state-based inspection.


\section{Attack Characterization}

% TODO:
% 1. Analyze the structure of a "recursion bomb" in UPER.
% 2. Explain why traditional entropy-based filters might fail or succeed.
% 3. Discuss the "amplification factor" of structural attacks on CPU cycles.

% Figure Placeholder:
% Insert local_Unpatched_Filter_Scaling.png here (as a conceptual representation of attack impact)

\section{Proposed Mechanism}

To balance the requirement for extreme security against CWE-674 structural attacks with the stringent low-latency constraints of V2X communications, we propose a two-tiered defense architecture: the \textit{Parser-Layer Circuit Breaker}. The system consists of a lightweight $\mathcal{O}(N)$ structural anomaly detector and an Adaptive FSM that dynamically modulates the inspection intensity. This design ensures that the MEC processing node remains resilient to resource exhaustion without imposing a continuous "inspection tax" on legitimate, time-sensitive traffic.

\subsection{System Overview}
The proposed mechanism is designed to reside at the network edge, specifically within the presentation-layer ingress of an MEC node or a high-performance RSU. The core philosophy is to decouple the expensive ASN.1 parsing operation from the initial packet ingestion. By performing a rapid, entropy-aware structural scan before the payload reaches the recursive parser, the system can identify and discard "structural bombs" with minimal computational overhead. The Adaptive FSM acts as the supervisory logic, utilizing threat intelligence from the anomaly detector to switch between low-overhead sampling and high-assurance strict inspection.

\subsection{O(N) Structural Frequency Anomaly Detector}

Legitimate V2X messages, containing cryptographic signatures and certificates, exhibit high entropy across their bit-streams. Statistically, long sequences of identical bytes are highly improbable in these payloads. Conversely, structural attacks in UPER-encoded ASN.1 rely on repetitive structural padding (e.g., repeating choice indices or length determinants) to construct deeply nested object trees within MTU limits. 

Algorithm \ref{alg:filter} defines the proposed structural anomaly detector. Unlike signature-based systems, this detector monitors the frequency of consecutive identical bytes, providing a generalized defense against mutated recursion payloads.

\begin{algorithm}[htbp]
\caption{O(N) Structural Frequency Anomaly Detector}
\label{alg:filter}
\begin{algorithmic}[1]
\REQUIRE $Payload$: Raw byte array of the incoming packet
\REQUIRE $T_{thresh}$: Threshold for consecutive identical bytes (e.g., 10)
\ENSURE \textbf{True} if anomalous, \textbf{False} otherwise
\IF{$Payload$ is empty}
    \RETURN \textbf{False}
\ENDIF
\STATE $Count \gets 1$
\STATE $CurrentByte \gets Payload[0]$
\FOR{$i = 1$ \TO $length(Payload) - 1$}
    \IF{$Payload[i] == CurrentByte$}
        \STATE $Count \gets Count + 1$
        \IF{$Count > T_{thresh}$}
            \RETURN \textbf{True} \COMMENT{Structural anomaly detected}
        \ENDIF
    \ELSE
        \STATE $CurrentByte \gets Payload[i]$
        \STATE $Count \gets 1$
    \ENDIF
\ENDFOR
\RETURN \textbf{False}
\end{algorithmic}
\end{algorithm}

\subsubsection{Computational Complexity}
\begin{itemize}
    \item \textbf{Time Complexity $\mathcal{O}(N)$:} The algorithm performs a single pass over the payload. For typical V2X messages ($N \approx 500$ bytes), execution time is sub-microsecond.
    \item \textbf{Space Complexity $\mathcal{O}(1)$:} The detection is performed in-place with constant memory overhead, avoiding the allocation-related jitter common in DPI.
\end{itemize}

\subsection{Adaptive Circuit Breaker FSM}

Continuous inspection of all packets introduces a persistent processing delay, which we define as the "inspection tax." To minimize this tax during nominal operations, we implement an Adaptive Circuit Breaker FSM (Fig. \ref{fig:fsm_diagram}).

\begin{figure}[htbp]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}[>=Stealth, node distance=5.5cm, on grid, auto,
                    every state/.style={draw=black, thick, minimum size=2.8cm, align=center}]
    
    \node[state, initial, initial text=Start, fill=green!5] (peace) {\textbf{PEACE\_TIME} \\ 5\% Sampling};
    \node[state, fill=red!5] (attack) [right=of peace] {\textbf{UNDER\_ATTACK} \\ 100\% Inspection \\ Cooldown: $C_{max}$};

    \path[->, thick]
        (peace) edge [bend left=20] node[above, align=center, font=\small] {Anomaly Detected \\ (Trigger Breaker)} (attack)
        (peace) edge [loop above] node[align=center, font=\small] {Normal Traffic \\ (Pass)} (peace)
        (attack) edge [bend left=20] node[below, align=center, font=\small] {Cooldown $\le 0$ \\ (Threat Mitigated)} (peace)
        (attack) edge [loop above] node[align=center, font=\small] {Anomaly Detected \\ (Reset Cooldown)} (attack);
        
\end{tikzpicture}
}
\caption{State Transition Diagram of the Adaptive Circuit Breaker FSM.}
\label{fig:fsm_diagram}
\end{figure}

\subsubsection{State Transitions and Dynamics}
The FSM (Algorithm \ref{alg:fsm}) maintains system throughput during \textit{Peace Time} by sampling only a fraction ($R_{sample}$) of traffic. The primary operational modes are:
\begin{itemize}
    \item \textbf{PEACE\_TIME:} The system operates in a low-overhead monitoring state. This probabilistic sampling ensures that the MEC node preserves its high-throughput processing capability, effectively eliminating the background inspection tax during normal conditions.
    \item \textbf{UNDER\_ATTACK:} Upon detection of a structural anomaly by the $\mathcal{O}(N)$ detector, the "circuit breaker" triggers. The FSM transitions to this high-assurance state, enforcing 100\% strict inspection for all packets and initiating a cooldown timer ($C_{max}$). 
\end{itemize}

The transition back to \textit{PEACE\_TIME} occurs when the cooldown period expires without further incident. Any subsequent anomaly detection resets the timer, ensuring persistent protection during sustained attacks.

\begin{algorithm}[htbp]
\caption{Adaptive Circuit Breaker FSM}
\label{alg:fsm}
\begin{algorithmic}[1]
\REQUIRE $Packet$: Incoming packet
\REQUIRE $R_{sample}$: Sampling rate during peace time (e.g., 5\%)
\REQUIRE $C_{max}$: Cooldown threshold (e.g., 10000 packets)
\STATE \textbf{Global State:} $State \in \{PEACE, ATTACK\}$
\STATE \textbf{Global Variables:} $Cooldown \gets 0$, $TotalPackets \gets 0$

\STATE $TotalPackets \gets TotalPackets + 1$
\STATE $DropPacket \gets$ \textbf{False}

\IF{$State == PEACE$}
    \IF{$TotalPackets \pmod{(100 / R_{sample})} == 0$}
        \STATE $DropPacket \gets$ \textsc{AnomalyDetector}($Packet$)
        \IF{$DropPacket ==$ \textbf{True}}
            \STATE $State \gets ATTACK$
            \STATE $Cooldown \gets C_{max}$
        \ENDIF
    \ENDIF
\ELSIF{$State == ATTACK$}
    \STATE $DropPacket \gets$ \textsc{AnomalyDetector}($Packet$)
    \IF{$DropPacket ==$ \textbf{True}}
        \STATE $Cooldown \gets C_{max}$
    \ELSE
        \STATE $Cooldown \gets Cooldown - 1$
        \IF{$Cooldown \le 0$}
            \STATE $State \gets PEACE$
        \ENDIF
    \ENDIF
\ENDIF
\RETURN $DropPacket$
\end{algorithmic}
\end{algorithm}

\subsubsection{FSM Complexity and Inspection Tax Minimization}
The FSM introduces negligible overhead, requiring only a modulo operation ($\mathcal{O}(1)$) and a conditional branch per packet during peace time. The overall system time complexity dynamically scales between $\mathcal{O}(1)$ (for unsampled packets) and $\mathcal{O}(N)$ (for inspected packets). By using an FSM with probabilistic sampling, we amortize the inspection cost, minimizing the MEC node's background resource footprint and ensuring the stability of safety-critical V2X services.


\section{Experimental Setup}

To evaluate the effectiveness and performance overhead of the proposed Parser-Layer Circuit Breaker, we constructed a local MEC testbed simulating a high-throughput V2X processing pipeline. The evaluation methodology focuses on measuring parsing latency, jitter, and system resilience under varying attack intensities.

\subsection{Hardware and Software Environment}
% TODO: Insert CPU model, core count, and clock frequency for the MEC server.
% TODO: Insert RAM specifications and OS kernel version.
The experimental testbed relies on a dedicated edge server to simulate the MEC processing node. To isolate parser performance and eliminate network-layer transmission noise, all tests were executed using a high-fidelity local loopback environment. 

The software stack is built upon Vanetza, an open-source implementation of the ETSI C-ITS protocol suite % TODO: Add Vanetza citation. 
Vanetza handles the processing of incoming CAM and DENM payloads, utilizing the underlying \texttt{asn1c} compiler for ASN.1 UPER decoding. We developed a custom testing framework, \texttt{qos-harness}, integrated directly into the Vanetza ingress pipeline to inject traffic and precisely measure presentation-layer latency.

\subsection{Traffic Generation and Attack Modalities}
We evaluated the system using a mix of legitimate V2X traffic and malicious CWE-674 recursion payloads. 
% TODO: Specify the baseline CAM/DENM dataset source or generation parameters.
To emulate a compromised OBU injecting structural attacks, we generated malicious UPER payloads designed to exploit deep nesting vulnerabilities within the IEEE 1609.2 certificate structures. The attack traffic was interleaved with legitimate traffic at varying injection rates (1\%, 5\%, and 10\%) to simulate different threat intensities.

To comprehensively assess the defense mechanisms, we defined three primary operational configurations:
\begin{itemize}
    \item \textbf{Mode 0 (Unpatched Native):} The baseline Vanetza parser operating without any recursion-depth limits or edge-layer pre-filtering. This represents the maximally vulnerable state.
    \item \textbf{Mode 1 (Official Patch):} The parser updated with application-layer security patches (e.g., static recursion depth limits in \texttt{asn1c}), but lacking the proposed edge-layer circuit breaker.
    \item \textbf{Mode 2 (Hybrid Defense):} The proposed defense-in-depth architecture, combining the Mode 1 application-layer patch with our $\mathcal{O}(N)$ Adaptive Circuit Breaker FSM at the network edge.
\end{itemize}

\subsection{Evaluation Metrics and Methodology}
The primary objective of the MEC node is to maintain deterministic processing times for safety-critical messages. Therefore, our evaluation focuses on micro-benchmarking the parser's execution time per packet.

We recorded the processing latency for millions of injected packets. To analyze the systemic impact of structural attacks, we extracted the following metrics:
\begin{itemize}
    \item \textbf{Mean and Median Latency:} To assess the baseline "inspection tax" and nominal processing overhead.
    \item \textbf{P99 Tail Latency:} To quantify the worst-case processing delays experienced by the 99th and 99.9th percentile of packets, which is critical for evaluating HoL blocking severity.
    \item \textbf{Max Latency:} To measure the absolute peak delay, particularly relevant for observing the "first-miss" impact before the FSM transitions to the \textit{UNDER\_ATTACK} state.
\end{itemize}

Jitter analysis was conducted by observing the variance in the P99 tail latency distribution. By clamping the P99 metrics, we can quantitatively demonstrate the circuit breaker's ability to preserve QoS and prevent catastrophic jitter in the MEC processing pipeline.

\section{Evaluation}

\subsection{QoS Impact of Parser Exhaustion}

We first evaluated the baseline QoS performance of the MEC node without any adversarial traffic. In the nominal state, the Vanetza parser achieves a mean processing latency of 0.0155 ms with a P99 tail latency of 0.0312 ms. This represents the reference state for our evaluation of parser pipeline resilience.

Under steady-state adversarial traffic, the Unpatched Native parser (Mode 0) demonstrates severe performance degradation. As shown in Table \ref{tab:unpatched}, increasing the attack injection rate from 1\% to 10\% results in a linear escalation of P99 tail latency. At a 10\% attack intensity, the P99 latency reaches 0.1811 ms, a six-fold increase over the baseline. The catastrophic Max latency of 0.6421 ms indicates severe HoL blocking, where legitimate packets are significantly delayed by recursive expansion events.

The integration of the proposed pre-filter effectively isolates the parser from these structural bombs. Even at 10\% attack intensity, the \textit{Filter} configuration suppresses the P99 tail latency to 0.0362 ms, closely approximating the baseline distribution. This confirms the efficacy of entropy-based structural scanning in maintaining tail latency control under high-load adversarial conditions.

\begin{table}[htbp]
\caption{Local QoS Performance Metrics (Unpatched Environment)}
\label{tab:unpatched}
\centering
\begin{tabular}{@{}lrrrrr@{}}
\toprule
\textbf{Scenario} & \textbf{Mean} & \textbf{Median} & \textbf{P99} & \textbf{P99.9} & \textbf{Max} \\
\midrule
Baseline & 0.0155 & 0.0145 & 0.0312 & 0.1106 & 0.1470 \\
Native (1.0\%) & 0.0172 & 0.0148 & 0.1435 & 0.1899 & 0.3920 \\
Native (5.0\%) & 0.0238 & 0.0152 & 0.1719 & 0.2845 & 0.5290 \\
Native (10.0\%) & 0.0315 & 0.0155 & 0.1811 & 0.2993 & 0.6421 \\
\addlinespace
Filter (1.0\%) & 0.0171 & 0.0156 & 0.0418 & 0.1778 & 0.2697 \\
Filter (5.0\%) & 0.0161 & 0.0155 & 0.0376 & 0.1641 & 0.3356 \\
Filter (10.0\%) & 0.0160 & 0.0163 & 0.0362 & 0.1686 & 0.3229 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Defense-in-Depth Comparison}

Table \ref{tab:patched} details the performance of the Mode 1 configuration (Official Patch). While the application-layer patch prevents infinite recursion, it introduces a deterministic inspection cost. The error-handling logic and recursion depth checks contribute to a slightly higher median latency (0.0168 ms vs. 0.0145 ms baseline). However, the patch successfully prevents the catastrophic 0.6 ms outliers seen in Mode 0, clamping the Max latency to 0.1981 ms under 10\% attack.

The $\mathcal{O}(N)$ pre-filter demonstrates a lower amortized overhead compared to the full application-layer patch. By identifying anomalies before the bit-stream is fully expanded, the pre-filter reduces the total CPU cycles consumed per malicious packet.

\begin{table}[htbp]
\caption{Local QoS Evaluation Table (Patched Environment)}
\label{tab:patched}
\centering
\begin{tabular}{@{}lrrrrr@{}}
\toprule
\textbf{Scenario} & \textbf{Mean} & \textbf{Median} & \textbf{P99} & \textbf{P99.9} & \textbf{Max} \\
\midrule
Baseline & 0.0162 & 0.0154 & 0.0313 & 0.1132 & 0.3388 \\
Native (1.0\%) & 0.0167 & 0.0158 & 0.0339 & 0.1437 & 0.2800 \\
Native (5.0\%) & 0.0169 & 0.0156 & 0.0432 & 0.1384 & 0.3594 \\
Native (10.0\%) & 0.0166 & 0.0159 & 0.0390 & 0.1200 & 0.1981 \\
\addlinespace
Filter (1.0\%) & 0.0178 & 0.0167 & 0.0358 & 0.1075 & 0.3659 \\
Filter (5.0\%) & 0.0171 & 0.0170 & 0.0349 & 0.0958 & 0.1786 \\
Filter (10.0\%) & 0.0160 & 0.0168 & 0.0320 & 0.1150 & 0.4987 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{First-Miss Penalty and Hybrid Defense}

A critical finding in our system jitter analysis is the "First-Miss Penalty." This phenomenon occurs when a structural attack packet is injected during the \textit{PEACE\_TIME} sampling window but is not selected for inspection (95\% probability). This packet reaches the parser, triggering a high-latency event before the FSM can transition to the \textit{UNDER\_ATTACK} state. In the \textit{Unpatched + Filter} configuration, this resulted in a Max latency spike of 0.3229 ms (Table \ref{tab:master}).

The \textit{Patched + Filter (Hybrid)} configuration (Mode 2) represents the most resilient architecture. By combining the edge-layer circuit breaker with the application-layer patch, we achieve the lowest overall Mean latency (0.0160 ms). The circuit breaker handles over 90\% of the adversarial load with near-zero overhead, while the official patch serves as a fallback to mitigate the impact of any packets that bypass the probabilistic sampling window. This defense-in-depth approach ensures that the MEC node remains stable even under stateful adversarial traffic designed to probe sampling gaps.

\begin{table}[htbp]
\caption{System-Wide QoS Comparison (10\% Attack Rate)}
\label{tab:master}
\centering
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrrrr@{}}
\toprule
\textbf{Scenario} & \textbf{Mean} & \textbf{Median} & \textbf{P99} & \textbf{P99.9} & \textbf{Max} \\
\midrule
Baseline (No Attack) & 0.0155 & 0.0145 & 0.0312 & 0.1106 & 0.1470 \\
Unpatched Native & 0.0315 & 0.0155 & 0.1811 & 0.2993 & 0.6421 \\
Unpatched + Filter & 0.0160 & 0.0163 & 0.0362 & 0.1686 & 0.3229 \\
Official Patch Native & 0.0166 & 0.0159 & 0.0390 & 0.1200 & 0.1981 \\
\textbf{Patched + Filter (Hybrid)} & \textbf{0.0160} & \textbf{0.0168} & \textbf{0.0320} & \textbf{0.1150} & \textbf{0.4987} \\
\bottomrule
\end{tabular}%
}
\end{table}

% Figure Placeholder:
% Insert master_defense_comparison.pdf here

\subsection{Adaptive Recovery Dynamics}

To assess recovery stability, we subjected the system to pulse attacks (high-intensity bursts followed by dormancy). The FSM's ability to return to the \textit{PEACE\_TIME} state after 10,000 legitimate packets ensures that the MEC node does not suffer from long-term "inspection lock-in" after a threat has dissipated.

% Figure Placeholder:
% Insert periodic_recovery_timeline.png here

% Figure Placeholder:
% Insert pulse_recovery_timeline.png here

As shown in the recovery timelines, the system achieves millisecond-level transition times once the circuit breaker is triggered. During the \textit{UNDER\_ATTACK} phase, the 100\% inspection policy ensures that no further structural bombs reach the parser, effectively preserving the QoS of the legitimate traffic stream. The cooldown mechanism prevents premature state oscillations, providing a stable transition back to the sampling-based monitoring mode. This stateful behavior is crucial for defending against intermittent adversarial traffic that attempts to exploit the transition boundaries of the defense system.


\section{Discussion}

The experimental results validate the efficacy of the proposed Parser-Layer Circuit Breaker in maintaining deterministic QoS under structural complexity attacks. However, a robust systems-security evaluation requires a nuanced discussion of the mechanism's boundaries, inherent trade-offs, and practical deployment considerations within MEC environments.

\subsection{System Jitter and Inspection Tax}
Traditional defenses require line-rate DPI, which imposes a constant "inspection tax" on every packet, increasing jitter for safety-critical V2X services. By using an FSM with probabilistic sampling, we amortize the inspection cost. During peace time, the effective complexity is reduced from $\mathcal{O}(N)$ to $\mathcal{O}(R_{sample} \times N)$, which is approximately $\mathcal{O}(0.05N)$, minimizing the MEC node's background resource footprint. This low-overhead filtering approach is critical for high-throughput edge nodes where compute resources are heavily contested.

\subsection{Tail Latency Control in MEC}
In V2X, the 99th percentile latency is often more critical than the mean. Structural attacks specifically target the "tail," causing extreme outliers that can disrupt cooperative awareness. Our results show that the circuit breaker mechanism effectively clamps the tail latency, preventing HoL blocking from cascading through the MEC processing pipeline. By discarding structural bombs before recursive expansion, the system ensures that legitimate time-sensitive packets are processed deterministically.

\subsection{False Positives and Generalizability Limitations}
The $\mathcal{O}(N)$ anomaly detector relies on the statistical improbability of long sequences of identical bytes in high-entropy payloads like signed UPER certificates. While highly effective for ASN.1 UPER, this heuristic may exhibit false positives if applied to protocols that natively utilize extensive structural padding or zero-byte initialization (e.g., certain legacy industrial protocols). The repetition threshold ($T_{thresh}$) must be carefully tuned to the empirical distribution of the target protocol. Furthermore, this mechanism is strictly a parser-layer defense; it does not provide universal protection against semantic logic flaws, cryptographic vulnerabilities, or broad volumetric DDoS attacks.

\subsection{The First-Miss Penalty and Hybrid Defense Strategy}
A fundamental limitation of any probabilistic sampling defense is the "first-miss penalty." As observed in the \textit{Unpatched + Filter} scenario, stateful adversarial traffic can exploit the $1 - R_{sample}$ sampling gap during \textit{PEACE\_TIME}, resulting in a high-latency event before the FSM transitions to \textit{UNDER\_ATTACK}. To address this, we strongly advocate for a hybrid defense strategy. Deploying the edge-layer circuit breaker to filter the vast majority of the adversarial load, while maintaining application-layer static recursion limits as a fallback, provides optimal parser pipeline resilience. This ensures that the rare packet bypassing the sample window is caught by the deterministic parser constraint, effectively suppressing the maximum latency spike.

\subsection{Stateful Adversarial Behavior and MEC Deployment Feasibility}
Advanced adversaries might employ "low-frequency" or stateful attack patterns designed to trigger the circuit breaker just frequently enough to maintain the \textit{UNDER\_ATTACK} state, thereby forcing the MEC node to incur the $\mathcal{O}(N)$ inspection tax continuously. However, as demonstrated in our complexity analysis, the $\mathcal{O}(N)$ operation is computationally inexpensive and non-allocating. Therefore, even under a sustained stateful attack, the MEC node experiences only a minor baseline shift rather than catastrophic HoL blocking. The practical feasibility of deploying this mechanism in production MEC environments is high, given its minimal memory footprint and compatibility with existing V2X ingress pipelines.

\section{Limitations and Future Work}

% TODO:
% 1. Discuss the limitation of structural repetition thresholds in non-UPER parsers.
% 2. Explore the potential of hardware-accelerated (FPGA/XDP) pre-filtering.
% 3. Address the possibility of "low-frequency" structural attacks designed to stay below the sampling rate.

\section{Conclusion}

% TODO:
% 1. Reiterate the effectiveness of the Parser-Layer Circuit Breaker.
% 2. Summarize the QoS gains (P99 suppression).
% 3. Final recommendation for MEC-enabled V2X deployments.

This paper presented a Parser-Layer Circuit Breaker designed to protect V2X MEC nodes from ASN.1 structural complexity attacks. By combining an $\mathcal{O}(N)$ entropy-based detector with an adaptive sampling FSM, we demonstrated a defense mechanism that preserves QoS while maintaining minimal overhead during normal operation. The proposed Hybrid Defense strategy effectively mitigates the "First-Miss Penalty," providing a robust framework for securing high-performance V2X systems against parser-layer resource exhaustion.

\end{document}
